ForestClaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-02-26 docs/parco13/abstract.tex
Continue working

Now combine.

@@

>>>>

The starting point of our work is defined by the p4est algorithms for
forest-of-octrees AMR on the one hand, and the Clawpack algorithms for the
numerical solution of hyperbolic conservation laws
% on uniformly gridded domains
on the other.  Both are specialized codes with the following characteristics:
\begin{center}
\begin{tabular}{l|l|l}
& \multicolumn{1}{c|}{\texttt{p4est}} & \multicolumn{1}{c}{Clawpack} \\
\hline
subject & hexahedral nonconforming mesh &  hyperbolic PDE on $[0, 1]^d$ \\
structure & forest of octrees & patch of $m^d$ DOFs \\
atomic unit & octree leaf & one DOF \\
parallelization & MPI & threads \\
memory access & distributed & shared \\
data type & integers & floating point values \\
language & C & Fortran 77 \\
dependencies & none & none \\
\hline
\end{tabular}
\end{center}
The proposed 1:1 correspondence between a leaf and a patch thus combines two
hithertwo disjoint models in a modular way that permits the reuse of existing,
verified and performant codes if the integration is done well.  The resulting
parallel programming model is a hybrid and often referred to as MPI+X.

Multiblock handling

Identification: an octree is a block, and a leaf is a patch.

Each block is understood as a reference unit cube with an optional per-block
geometric mapping.  The coordinate system of

Information provided by the mesh:
Sequence of blocks, list of patches for each.  Each patch
has a list of neighbor patches including information on

@@

\section*{Acknowledgements}

The authors acknowledge valuable discussion with Randy LeVeque, Marsha Berger,
and Hans-Petter Langtangen.  The leaf/grid paradigm was independently presented
by B.\ as part of a talk at the SCI Institute, Utah, in July 2011.
